On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-22 paper/paper.tex
Added a TODO note about an alternate implementation of 'runIter'

>>>>

\begin{todo}
  \ttt{runIter} has the following alternate implementation. Would this be
  useful to use somewhere?

  \begin{lstlisting}
  runIter f = getDone . fix (f >=>)

  getDone :: Iter b a -> b
  getDone (Done x) = x
  getDone _ = error "getDone"
  \end{lstlisting}

  Maybe this could be useful in some proofs or derivations somewhere (in this
  paper or elsewhere)?

  Note that \verb|error| is never called under any circumstance in this
  implementation of \verb|runIter|.
\end{todo}
